Stochastic Variance-Reduced Policy Gradient

### 2018-02-09 svrpg.tex
Updated

\section{Practical SVRPG versions}\label{app:practicalsvrpg}
\begin{algorithm}[h]
        \begin{algorithmic}
        \STATE \textbf{Input:} A gradient estimate $g_t$ and parameters $\beta_1$, $\beta_2$, $\epsilon$ and $\alpha$.
        \STATE $m_t = \beta_1 m_{t-1} + (1 - \beta_1) g_t$
        \STATE $v_t = \beta_2 v_{t-1} + (1 - \beta_2) g_t \circ g_t$ ($\circ$ is the Hadamard (component-wise) product)
        \STATE $\hat{m}_t = \dfrac{m_t}{1 - \beta^t_1}$
        \STATE $\hat{v}_t = \dfrac{v_t}{1 - \beta^t_2}$
        \STATE $\Delta(g_t) = \dfrac{\alpha}{\sqrt{\hat{v}_t} + \epsilon} \hat{m}_t$
        \STATE \textbf{Return:} The increment $\Delta(g_t)$  of the parameters.
\end{algorithmic}
 \caption{
 \label{A:adam}
 Adam}
\end{algorithm}
\subsection{Learning Rates}
Let us give a deeper insight on the two different learning rate used by our algorithm. We have already said that we use two different ADAM one related to the snapshots and another one related to the sub-iterations. In this way tha ADAM associated to the snapshots will take into account only the snapshots history through the parameters $m_{t-1}$ and $v_{t-1}$. The same reasoning holds for the sub-iterations. This, of course, allows our algorithm to take into account the different variabilities in a more accurate manner.
\subsection{Baseline}
For all batch gradient-based algorithms, we use the same time-varying feature encoding for the linear baseline:
\begin{align*}
\psi_{s,t}=concat(s, s \odot s, 0.01t, (0.01t)^2, (0.01t)^3,1)
\end{align*}
where $s$ is the state vector and $\odot$ is the element-wise product.
\section{Experimental Details}\label{app:exp}
Used environments:
\begin{enumerate}
	\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, cart velocity $\dot{x}$ and pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. The episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time steps T is greater than 100.
	\item \emph{Mujoco Swimmer}: 13-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
	\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
\end{enumerate}

Refer to \cite{duan2016benchmarking}  for more details about GPOMDP in Half Cheetah task.
All the experiments' parameters are reported in the following table:

\centering
\begin{tabular}{| l | c  c  c |}
	\hline	
	& Cart-Pole & Swimmer & Half Cheetah \\
	\hline
	State space dimension  & 4 & 13 & 20 \\
	Control space dimension & 1 & 2 & 6 \\
	NN Hidden layers & 8 & 32x32 & 100x50x25 \\
	Adam learning rate SVRPO & $5\cdotp10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
	Adam learning rate GPOMDP & $10^{-2}$ & $10^{-3}$ & $10^{-2}$ \\
	Snapshot batch size & 100 & 100 & 100 \\
	Sub-iterations batch size & 10 & 10 & 10 \\
	GPOMDP batch size & 10 & 10 & 100 \\
	Max number of sub-iterations & 50 & 20 & 20 \\
	Episodes horizon& 100 & 500 & 500 \\
	Baseline& No & No & Yes \\
	Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
	Total number of trajectories& 10000 & 20000 & 50000 \\
	\hline  
\end{tabular}

>>>>

\section{Practical SVRPG versions}\label{app:practicalsvrpg}
\begin{algorithm}[h]
        \begin{algorithmic}
        \STATE \textbf{Input:} A gradient estimate $g_t$ and parameters $\beta_1$, $\beta_2$, $\epsilon$ and $\alpha$.
        \STATE $m_t = \beta_1 m_{t-1} + (1 - \beta_1) g_t$
        \STATE $v_t = \beta_2 v_{t-1} + (1 - \beta_2) g_t \circ g_t$ ($\circ$ is the Hadamard (component-wise) product)
        \STATE $\hat{m}_t = \dfrac{m_t}{1 - \beta^t_1}$
        \STATE $\hat{v}_t = \dfrac{v_t}{1 - \beta^t_2}$
        \STATE $\Delta(g_t) = \dfrac{\alpha}{\sqrt{\hat{v}_t} + \epsilon} \hat{m}_t$
        \STATE \textbf{Return:} The increment $\Delta(g_t)$  of the parameters.
\end{algorithmic}
 \caption{
 \label{A:adam}
 Adam}
\end{algorithm}
\subsection{Learning Rates}
Let us give a deeper insight on the two different learning rate used by our algorithm. We have already said that we use two different ADAM one related to the snapshots and another one related to the sub-iterations. In this way tha ADAM associated to the snapshots will take into account only the snapshots history through the parameters $m_{t-1}$ and $v_{t-1}$. The same reasoning holds for the sub-iterations. This, of course, allows our algorithm to take into account the different variabilities in a more accurate manner.
\subsection{Baseline}
For all batch gradient-based algorithms, we use the same time-varying feature encoding for the linear baseline:
\begin{align*}
        \psi(s,t)=concat(s, s \odot s, 0.01t, (0.01t)^2, (0.01t)^3,1)
\end{align*}
where $s$ is the state vector and $\odot$ is the element-wise product.
As a consequence, the baseline for both SVRPG and G(PO)MDP is defined as follows:
\[
        b(s,a) = \transpose{\boldsymbol{\lambda}} \psi(s,t)
\]
\section{Experimental Details}\label{app:exp}
Used environments:
\begin{enumerate}
	\item \emph{Cart-Pole Balancing} : 4-dimensional state space: cart position x, pole angle $\theta$, cart velocity $\dot{x}$ and pole velocity $\dot{\theta}$; 1-dimensional action space: the horizontal force applied to the cart body. Reward function  is defined as $r(s, a) := 10 - (1 - cos(\theta)) - 10^{-5}\norm[] a^2$. The episodes terminates when $|x|>2.4$ or $|\theta|>0.2$ or the number of time steps T is greater than 100.
	\item \emph{Mujoco Swimmer}: 13-dimensional state space: 3 links velocities ($v_x$ and $v_y$ of center of masses) and 2 actuated joints angles. 2-dimensional action space: the two momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 10^{-4}\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
	\item \emph{Mujoco Half Cheetah}: 20-dimensional state space: 9 links and 6 actuated joints angles. 6-dimensional action space: the 6 momentums applied on actuated joints.  The reward function is defined as $r(s, a) := v_x - 0.05\norm[2] a^2$. The episodes terminates when the number of time steps T is greater than 500.
\end{enumerate}

Refer to \cite{duan2016benchmarking}  for more details about GPOMDP in Half Cheetah task.
All the experiments' parameters are reported in Table~\ref{T:exp_settings}.

\begin{table}[b]
\centering
\caption{Settings of the experiments.}
\label{T:exp_settings}
\begin{tabular}{| l | c  c  c |}
	\hline	
	& Cart-Pole & Swimmer & Half Cheetah \\
	\hline
	State space dimension  & 4 & 13 & 20 \\
	Control space dimension & 1 & 2 & 6 \\
	NN Hidden layers & 8 & 32x32 & 100x50x25 \\
	Adam learning rate SVRPO & $5\cdotp10^{-2}$ & $10^{-3}$ & $10^{-3}$ \\
	Adam learning rate GPOMDP & $10^{-2}$ & $10^{-3}$ & $10^{-2}$ \\
	Snapshot batch size & 100 & 100 & 100 \\
	Sub-iterations batch size & 10 & 10 & 10 \\
	GPOMDP batch size & 10 & 10 & 100 \\
	Max number of sub-iterations & 50 & 20 & 20 \\
	Episodes horizon& 100 & 500 & 500 \\
	Baseline& No & No & Yes \\
	Discount $(\gamma)$& 0.99 & 0.995 & 0.99 \\
	Total number of trajectories& 10000 & 20000 & 50000 \\
	\hline  
\end{tabular}
\end{table}
In Figure~\ref{fig:cartpole_big},~\ref{fig:swimmertwo_big} and~\ref{fig:swimmerone_big} we have reported the same results presented in the main paper but on bigger figures.

\begin{figure}[t]
        \centering
    \begin{minipage}[t]{0.48\textwidth}
	\includegraphics[width=.98\textwidth]{images/cart_pole_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of SVRPG vs G(PO)MDP in the Cart-pole task, with 90\% t-student confidence intervals.}
	\label{fig:cartpole_big}
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.48\textwidth}
	\includegraphics[width=0.98\textwidth]{swimmer_self_normalized_SVRPG_vs_SVRPG_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs unbiased SVRPG in the Swimmer task, with 90\% confidence intervals.}
	\label{fig:swimmertwo_big}
    \end{minipage}
\end{figure}
\begin{figure}[t]
        \centering
	\includegraphics[width=0.47\textwidth]{swimmer_self_normalized_SVRPG_vs_GPOMDP_tex.pdf}
	\caption{On-line performance over sampled trajectories of self-Normalized SVRPG vs G(PO)MDP in the Swimmer task, with 90\% confidence intervals}
	\label{fig:swimmerone_big}
\end{figure}
